Paper

### 2021-12-14 Paper.Rmd
Minor edit

```{r}
set.seed(400)
plot_dat1 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=20, prop_vac = 0)

>>>>

Compare different vaccination rates
```{r}
set.seed(400)
plot_dat1 <- get_bootstrap_cis(days=50, num_subjects=200, x_dim=1, y_dim=1, I_0=1, inf_dist=0.1, sample_size=20, prop_vac = 0)
